Who will win the US 2024 election?!!

### 2024-03-14 paper/paper.qmd
Updates

##Introduction to the Data:
With a focus on the American Community Survey (ACS) 2022 sample,
we present a summary of the dataset utilized in our statistical research study in this part.

Using a 1-in-100 national random sample, the ACS 2022 sample provides a thorough overview of the demographic,
socioeconomic, and geographic features of the US population. Most importantly, this dataset includes people who live in
both home and group quarters, offering a comprehensive view of the American population.

@@

All things considered, the ACS 2022 sample is a useful tool for statistical analysis and empirical study, providing
insights into the complex aspects of American culture. In the sections that follow, we explore the variables that make
up the dataset and consider how important they are to comprehending voting patterns and electoral results for the 2024 election
using this 20022 survey data.

@@

# Results

# Discussion

# Appendix

# References

>>>>

##Introduction to the Data:
With a focus on the American Community Survey (ACS) 2022 sample,
we present a summary of the dataset utilized in our statistical research study in this part.
Using a 1-in-100 national random sample, the ACS 2022 sample provides a thorough overview of the demographic,
socioeconomic, and geographic features of the US population. Most importantly, this dataset includes people who live in
both home and group quarters, offering a comprehensive view of the American population.

@@

All things considered, the ACS 2022 sample is a useful tool for statistical analysis and empirical study, providing
insights into the complex aspects of American culture. In the sections that follow, we explore the variables that make
up the dataset and consider how important they are to comprehending voting patterns and electoral results in relation
to the 2022 presidential election.

@@
